Paper_analyses

### 2021-08-02 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

  mutate(neutral_neg_mean_arousal = mean(ArousalMean, na.rm = TRUE),
                                         neutral_sd_mean_arousal = sd(ArousalMean, na.rm = TRUE)) %>%
  mutate(neutral_neg_mean_arousal_self = mean(arousal, na.rm = TRUE),
         neutral_neg_sd_arousal_self = sd(arousal, na.rm = TRUE))

@@

# compute new varoables where arousal is scaled to negative (negative value - mean of negative and neutral) same to positive
tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
    mutate_at(vars(matches('^neutral_pos_.*$')), ~ 
                  replace(., neutral_pos == FALSE, NA))

@@

>>>>

  mutate(neutral_neg_mean_arousal = mean(ArousalMean, na.rm = TRUE),
                                         neutral_neg_sd_arousal = sd(ArousalMean, na.rm = TRUE)) %>%
  mutate(neutral_neg_mean_arousal_self = mean(arousal, na.rm = TRUE),
         neutral_neg_sd_arousal_self = sd(arousal, na.rm = TRUE))

@@

# compute new variables where arousal is scaled to negative (negative value - mean of negative and neutral) same to positive
tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
    mutate_at(vars(matches('^neutral_pos_.*$')), ~ 
                  replace(., neutral_pos == FALSE, NA))

@@

tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean - tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal,
                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean - 
                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_mean_arousal, 
                                                                           tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean - mean(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean, na.rm = TRUE)))

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground))

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground), tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab)

library(tidyverse)

tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, ArousalMean))+
  geom_point()+
  stat_summary(geom = 'pointrange')

tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, arousal_rel_neutral_ground))+
  # geom_point()+
  stat_summary(geom = 'pointrange')

tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground_z <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal,
                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground / 
                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_sd_arousal, 
                                                                           tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ sd(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean, na.rm = TRUE)))

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground))
table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground), tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab)

tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, ArousalMean))+
  # geom_point()+
  # stat_summary(geom = 'pointrange')
 geom_boxplot()
tmp.df4_full_stim_downs_jun2021_60bins %>%
  group_by(stimIAPS, ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, arousal_rel_neutral_ground_z ))+
  # geom_point()+
  geom_boxplot()
  # stat_summary(geom = 'pointrange')
```
